Hydrodynamics and rheology of weakly adhesive vesicle doublets

### 2019-01-29 vesicle_code/docs/adhesion/adhesion.tex
added some subplots to fig 6

@@

\begin{figure}[htp]
  \begin{minipage}{0.6\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/angleDefinition.pdf}
  \end{minipage}
  \caption{\label{fig:extensionalPhaseDiagram} {\em Left}:Phase diagram
  of vesicle hydrodynamics in an extensional flow with a fixed Hamaker
  constant $H=0.7$ and adhesion length scale $\delta = 0.4$.  For small
  extensional rates, the doublet structure is not broken (blue marks),
  while at large extensional rates, the doublet is broken (red marks).
  The size of the round blue marks indicate the final inclination angle
  with the larger dots rotation less ($\theta=pi$) and the smaller dots
  rotating more ($\theta = pi/2$).  A square mark is used for
  simulations that did not result in a steady-state inclination angle in
  the given time horizon.  {\em Right}: The definition of the
  inclination angle.  An inclination angle of $\pi$ indicates a doublet
  whose long axis is parallel to the converging direction, while an
  inclination angle of $\pi/2$ indicates a doublet whose short axis is
  parallel to the converging direction.  The square mark is a stagnation
  point while the round point is located at the center of the vesicle.}
\end{figure}

@@

\begin{figure}[htp]
  \begin{minipage}{0.45\textwidth}
  \centering
  \includegraphics[height=\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\textwidth}
    \includegraphics[height=\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
  \end{minipage}
  \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
  inclination angle of a doublet formed by vesicles of reduced area
  $0.70$ submerged in an extensional flow with an extensional rate of
  $\chi$.  {\em Right}: The final inclination angle of doublets.
  Results are not reported for all the low extensional rates since the
  doublet had not tilted to a steady-state inclination angle for the
  given time horizon.}
\end{figure}

>>>>

The doublet starts at an angle of $\pi$ and rotates towards some number
less than $\pi/2$ (if it converges).

@@

\begin{figure}[htp]
  \begin{minipage}{0.63\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.35\textwidth}
    \centering
    \includegraphics[width=0.8\textwidth]{figs/angleDefinition.pdf}
    \includegraphics[height=0.45\textwidth]{figs/rotate1.pdf}
    \hfill
    \includegraphics[height=0.45\textwidth]{figs/rotate2.pdf}
  \end{minipage}
  \caption{\label{fig:extensionalPhaseDiagram} {\em Left}: Phase diagram
  of vesicle hydrodynamics in an extensional flow with a fixed Hamaker
  constant $H=0.7$ and adhesion length scale $\delta = 0.4$.  For small
  extensional rates, the doublet structure is not broken (blue marks),
  while at large extensional rates, the doublet is broken (red marks).
  The size of the round blue marks indicate the final inclination angle
  with the larger dots rotation less ($\theta=\pi$) and the smaller dots
  rotating more ($\theta = \pi/2$).  A square mark is used for
  simulations that did not result in a steady-state inclination angle in
  the given time horizon.  {\em Right}: The definition of the
  inclination angle.  An inclination angle of $\pi$ indicates a doublet
  whose long axis is parallel to the converging direction, while an
  inclination angle of $\pi/2$ indicates a doublet whose short axis is
  parallel to the converging direction.  The square mark is a stagnation
  point while the round point is located at the center of the vesicle.}
\end{figure}

@@

\begin{figure}[htp]
  \begin{minipage}{0.45\textwidth}
  \centering
  \includegraphics[height=0.8\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\textwidth}
    \includegraphics[height=0.8\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
  \end{minipage}
  \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
  inclination angle of a doublet formed by vesicles of reduced area
  $0.70$ submerged in an extensional flow with an extensional rate of
  $\chi$.  {\em Right}: The final inclination angle of doublets.
  Results are not reported for all the low extensional rates since the
  doublet had not tilted to a steady-state inclination angle for the
  given time horizon.}
\end{figure}
